Generating Random Logic Programs Using Constraint Programming

### 2019-12-31 paper/paper.tex
Small changes

\begin{itemize}
\item Heads are too restrictive: $\variable{P}(X, Y, X)$ should be allowed.
\item Formal definition (here and in the predicate invention paper): two
  predicates are independent if all of their groundings are independent.
\item A constraint for logical equivalence.
\item Perhaps negative cycle detection could use the same graph as the
  independence propagator? If we extend each domain to {-1, 0, 1}, but that
  might make propagation weaker or slower.
\item Could investigate how uniform the generated distribution of programs is.
  Distributions of individual parameters will often favour larger values
  because, e.g., there are more 5-tuples than 4-tuples.
\item Inference options to explore. Logspace vs normal space. Symbolic vs
  non-symbolic. Propagate evidence (might be irrelevant)? Propagate weights?
  Supported knowledge compilation techniques: sdd, sddx, bdd, nnf, ddnnf, kbest,
  fsdd, fbdd.
\item Mention the random heuristic. Mention that restarting gives better
  randomness, but duplicates become possible. Restarting after each run is
  expensive. Periodic restarts could be an option.
\end{itemize}

@@

\begin{figure}[t]
  \centering
  \begin{tikzpicture}
    \node[draw,circle,gray,text=black] (or) at (0, 0) {$\lor$};
    \node[draw,circle,gray,text=black] (not) at (-1, -1) {$\neg$};
    \node (P) at (-1, -2) {$\variable{P}(X)$};
    \node[draw,circle,gray,text=black] (and) at (1, -1) {$\land$};
    \node (Q) at (0, -2) {$\variable{Q}(X)$};
    \node (R) at (2, -2) {$\variable{P}(X)$};
    \draw[gray] (or) -- (not);
    \draw[gray] (or) -- (and);
    \draw[gray] (not) -- (P);
    \draw[gray] (and) -- (Q);
    \draw[gray] (and) -- (R);
  \end{tikzpicture}
  \label{fig:example_tree}
  \caption{A tree representation of the formula from \cref{example:formula}}
\end{figure}

\begin{example} \label{example:formula} % TODO: describe (and refer to the figure)
  Let $\maxNumNodes{} = 8$. Then $\neg\variable{P}(X) \lor (\variable{Q}(X)
  \land \variable{P}(X))$...
  \begin{alignat*}{8}
    \variable{treeStructure} &= [0, &&0, &&0, &&1, &&2, &&2, &&6, &&7],\\
    \variable{treeValues} &= [{\lor}, &&{\neg}, &&{\land}, \variable{P}(&&X), \variable{Q}(&&X), \variable{P}(&&X), &&\top, &&\top],\\
    \variable{numNodes} &= 6, && && && && && && &&\\
    \variable{numTrees} &= 3. && && && && && && &&
  \end{alignat*}
\end{example}

@@

\begin{constraint}
  $\variable{tree}(\variable{treeStructure}, \variable{numTrees})$, i.e.,
  \variable{treeStructure} represents \variable{numTrees} trees (dominator-based
  filtering \cite{DBLP:conf/cp/FagesL11}).
\end{constraint}

@@

>>>>

\begin{itemize}
\item Heads are too restrictive: $\variable{P}(X, Y, X)$ should be allowed.
\item A constraint for logical equivalence.
\item Perhaps negative cycle detection could use the same graph as the
  independence propagator? If we extend each domain to {-1, 0, 1}, but that
  might make propagation weaker or slower.
\item Could investigate how uniform the generated distribution of programs is.
  Distributions of individual parameters will often favour larger values
  because, e.g., there are more 5-tuples than 4-tuples.
\item Inference options to explore. Logspace vs normal space. Symbolic vs
  non-symbolic. Propagate evidence (might be irrelevant)? Propagate weights?
  Supported knowledge compilation techniques: sdd, sddx, bdd, nnf, ddnnf, kbest,
  fsdd, fbdd.
\item Mention the random heuristic. Mention that restarting gives better
  randomness, but duplicates become possible. Restarting after each run is
  expensive. Periodic restarts could be an option.
\end{itemize}

@@

\begin{figure}[t]
  \centering
  \begin{tikzpicture}
    \node[draw,circle,gray,text=black] (or) at (0, 0) {$\lor$};
    \node[draw,circle,gray,text=black] (not) at (-1, -1) {$\neg$};
    \node (P) at (-1, -2) {$\variable{P}(X)$};
    \node[draw,circle,gray,text=black] (and) at (1, -1) {$\land$};
    \node (Q) at (0, -2) {$\variable{Q}(X)$};
    \node (R) at (2, -2) {$\variable{P}(X)$};
    \draw[gray] (or) -- (not);
    \draw[gray] (or) -- (and);
    \draw[gray] (not) -- (P);
    \draw[gray] (and) -- (Q);
    \draw[gray] (and) -- (R);
  \end{tikzpicture}
  \caption{A tree representation of the formula from \cref{example:formula}}
  \label{fig:example_tree}
\end{figure}

\begin{example} \label{example:formula}
  Let $\maxNumNodes{} = 8$. Then $\neg\variable{P}(X) \lor (\variable{Q}(X)
  \land \variable{P}(X))$ corresponds to the tree in \cref{fig:example_tree} and
  can be encoded as:
  \begin{alignat*}{8}
    \variable{treeStructure} &= [0, &&0, &&0, &&1, &&2, &&2, &&6, &&7],\\
    \variable{treeValues} &= [{\lor}, &&{\neg}, &&{\land}, \variable{P}(&&X), \variable{Q}(&&X), \variable{P}(&&X), &&\top, &&\top],\\
    \variable{numNodes} &= 6, && && && && && && &&\\
    \variable{numTrees} &= 3. && && && && && && &&
  \end{alignat*}
  In the rest of this section, we will describe how the elements of
  $\variable{treeValues}$ are encoded and list a series of constraints that make
  this representation unique.
\end{example}

@@

\begin{constraint}
  \variable{treeStructure} represents \variable{numTrees} trees, i.e.,
  \[
    \variable{tree}(\variable{treeStructure}, \variable{numTrees})\footnote{This
      constraint uses dominator-based filtering by Fages and Lorca
      \cite{DBLP:conf/cp/FagesL11}.}.
  \]
\end{constraint}

@@

% TODO: define independence of predicates
% Formal definition (here and in the predicate invention paper): two
% predicates are independent if all of their groundings are independent.
